On the surprising effectiveness of a simple matrix exponential derivative approximation, with application to global SARS-CoV-2

### 2023-10-30 manuscript/pnas_revision.tex
final edits before resubmission

 \cref{sec:emp}, contains simulation studies comparing: accuracy of matrix exponential derivative approximations for different distributional assumptions on the generator matrix; the posterior distributions obtained using surrogate-trajectory Hamiltonian Monte Carlo \cref{sec:Sur:trad:HMC} and traditional Hamiltonian Monte Carlo; and parameter identification under different priors on generator matrix elements.

>>>>

 \cref{sec:emp} contains simulation studies comparing: accuracy of matrix exponential derivative approximations for different distributional assumptions on the generator matrix; the posterior distributions obtained using surrogate-trajectory Hamiltonian Monte Carlo (\cref{sec:Sur:trad:HMC}) and traditional Hamiltonian Monte Carlo; and parameter identification under different priors on generator matrix elements.
